In this section, we provide a qualitative evaluation of the item-item similarities learned by our I-\LinearLow model. 
We use \Fotolia, a dataset from a major stock image market site\footnote{\scriptsize The dataset sharing agreement with the provider restricts us from reporting the statistics and quantitative results. Hence, we do not report summary statistics and quantitative results on this dataset}.  
The data provides whether a given user has clicked on a particular image category, and from these our model can infer the similarity measure between
the image categories. Note that the similarity is inferred solely based on the click patterns, without doing any analysis of the textual content of
the category names.
We choose this dataset for the qualitative evaluation mainly because the items are category names and are much easier to interpret
compared to the other datasets.





% users clicks on various image categories. 
% Since the similarity metric is an important aspect of personalization, we evaluate the item-item similarities learned by I-\LinearLow  model on the \Fotolia dataset. 

In Table~\ref{tbl:similarity-evaluation}, we show some examples~\footnote{Download https://drive.google.com/file/d/0B-0mTXCErInJd1RUSXl3YlE4TVE/view?usp=sharing and view it in a browser for an interactive exploration of learned item-item similarities.} of top-5 similar items learned by I-\LinearLow model. We observe that the model 
discovers very meaningful and explainable similarities, hence making it very applicable in similar item recommendations.  
\begin{table*}
	\centering
	\caption{Top-5 similar items learned by I-\LinearLow model.}
	\label{tbl:similarity-evaluation}
	\setlength{\arrayrulewidth}{.2em}
	\resizebox{0.85\textwidth}{!}{%
		\begin{tabular}{llllllll}
		% \hline
		\hline
		\textbf{Item} & Chemistry & Chilling out & Workers & Unemployment & Divorce and Conflict & Museums\\
		\hline
		\multirow{5}{*}{\textbf{Similar items}} & Test and Analysis & Beach Holidays & Construction & Job Search & Depression & Painting \\
		& Drug and Pills & Tourism & Teamwork & Tax and Accounting & Getting upset & Statues\\
		& Health Care & Relaxing & Manufacturing & Breaking the law & Crying & Artistic monuments\\
		& Scientists & Hiking & Service industry & Money & Loneliness & Paris\\
		& Medical Equipments& Consumer service & Beaches& Workers&  Rage & Italy\\
		\hline
		\end{tabular}
		}
		\resizebox{0.85\textwidth}{!}{%

		\begin{tabular}{lllllllll}
		% \hline
		\hline
		\textbf{Item} & Dance & Vinegar & Pearls & Graduation& Aging & Homelessness & Lizards\\
		\hline
		\multirow{5}{*}{\textbf{Similar items}} & Exercise & Olive Oil & Wealth & High School & Patients & Depression & Dragons\\
		& Running And Jumping & Spice & Wedding & School & Grand Parenting & Loneliness& Snakes\\
		& Disco And Clubs & Salads & Accessories & Exams & Disability & Crying & Other\\
		& Circus And Performing & Garlic & Gold & Job Search & Health Care& Getting Upset& Butterflies\\
		& Gymnastics & other & Make Up& E-Learning& Doctors & Risk And Danger & Owls\\
		\hline
		\end{tabular}
	}
\end{table*}
